\item 
Let $\vec{A}$ be a $3 \times 3$ real matrix and $\vec{I}_3$ be the $3 \times 3$ identity matrix.  
Which of the following statements is NOT true?
\hfill (ST 2024)
\begin{enumerate}
\item If the row-reduced echelon form of $\vec{A}$ is $\vec{I}_3$, then zero is not an eigenvalue of $\vec{A}$
\item If zero is not an eigenvalue of $\vec{A}$, then the row-reduced echelon form of $\vec{A}$ is $\vec{I}_3$
\item If $\vec{A}$ has three distinct eigenvalues, then the row-reduced echelon form of $\vec{A}$ is $\vec{I}_3$
\item If the system $\vec{A} \vec{x} = \vec{b}$ has a solution for every $3\times 1$ real vector $\vec{b}$, then the row-reduced echelon form of $\vec{A}$ is $\vec{I}_3$
\end{enumerate}
\item 
Let $\vec{u}_1, \vec{u}_2, \vec{u}_3, \vec{v}_1, \vec{v}_2, \vec{v}_3$ be vectors in $\mathbb{R}^4$. Let $U$ be the span of $\{\vec{u}_1, \vec{u}_2, \vec{u}_3\}$ and $V$ be the span of $\{\vec{v}_1, \vec{v}_2, \vec{v}_3\}$.  

Statements:  
\begin{enumerate}[label=(\Roman*)]

	\item If $\dim\brak{U \cap V} = 2$ and $\dim\brak{U} = 3$, then $\cbrak{\vec{v}_1, \vec{v}_2, \vec{v}_3}$ is linearly dependent.  
	\item  If $U + V = \mathbb{R}^4$, then either $\brak{\vec{u}_1, \vec{u}_2, \vec{u}_3}$ is linearly independent or $\brak{\vec{v}_1, \vec{v}_2, \vec{v}_3}$ is linearly independent.
\end{enumerate}
Which is/are true?
\hfill (ST 2024)
\begin{enumerate}
\begin{multicols}{4}
\item Only (I)
\item Only (II)
\item Both (I) and (II)
\item Neither (I) nor (II)
\end{multicols}
\end{enumerate}
\item 
Consider $\mathbb{R}^2$ with standard inner product. If $\vec{u} = \myvec{ a \\ b }$ is such that  
$ \vec{u}^{\top} \myvec{ 1 \\ 2 }  = 2$  
and  
$ \vec{u}^{\top} \myvec{ 4 \\ -2 }  = -1$,  
then which statement is true?
\hfill (ST 2024)
\begin{enumerate}
\begin{multicols}{4}
\item $ \vec{u}^{\top} \myvec{ 1 \\ -1 }  = \frac12$
\item $ \vec{u}^{\top} \myvec{ -1 \\ 1 }  = \frac35$
\item $ \vec{u}^{\top} \myvec{ 2 \\ -\frac12 }  = -\frac65$
\item $ \vec{u}^{\top} \myvec{ -\frac12 \\ 1 }  = \frac45$
\end{multicols}
\end{enumerate}
\item 
Let $\vec{A} = \myvec{ a_1 & a_2 & a_3 \\ b_1 & b_2 & b_3 }$ be a $2\times 3$ real matrix with $\brak{a_1,a_2,a_3} \neq \brak{0,0,0}$, $\brak{b_1,b_2,b_3} \neq \brak{0,0,0}$, and $\mathrm{rank}\brak{\vec{A}} = 1$.  
Define:  
\begin{align*}
	W &= \cbrak{ \vec{x} \in \mathbb{R}^3 : \vec{A}\vec{x} = \vec{0} }  
	\\
	W_1 &= \brak{ \vec{x} \in \mathbb{R}^3 : a_1 x_1 + a_2 x_2 + a_3 x_3 = 0} 
	\\
W_2 &= \brak{\vec{x} \in \mathbb{R}^3 : b_1 x_1 + b_2 x_2 + b_3 x_3 = 0}
\end{align*}

Statements:  
\begin{enumerate}[label=(\Roman*)]
	\item $W = W_1 \cap W_2$  
	\item  $W_1 = W_2$
\end{enumerate}
Which is/are true?
\hfill (ST 2024)
\begin{enumerate}
\begin{multicols}{4}
\item Only (I)
\item Only (II)
\item Both (I) and (II)
\item Neither (I) nor (II)
\end{multicols}
\end{enumerate}
\item
Let $\vec{A}$ be an $n\times n$ real matrix. Which are true?
\hfill (ST 2024)

\begin{enumerate}
\item If $\vec{A}$ symmetric and $\vec{A}+\epsilon \vec{I}_n$ PSD for all $\epsilon>0$, then $\vec{A}$ is PSD  
\item If $n$ odd, then $\vec{A}-\vec{A}^\top$ not invertible  
\item If $\vec{A}$ symmetric and all singular values $>0$, then $\vec{A}$ positive definite  
\item If $1$ is the only singular value of $\vec{A}$, then $\vec{A}$ is orthogonal
\end{enumerate}
\item
Which statements are true?
\hfill (ST 2024)
\begin{enumerate}
\item If $\vec{A}$ is $3\times3$ real with 3 distinct eigenvalues, then $\vec{A}$ is diagonalizable
\item If $\vec{A}^2$ is diagonalizable, then $\vec{A}$ is diagonalizable
\item For real $a,b,c$, if $\myvec{0&a&b\\0&0&c\\0&0&0}$ is diagonalizable, then $a=b=c=0$
\item If $\vec{A}=\myvec{a&b&c\\0&d&e\\0&0&f}$ is diagonalizable, then $\vec{A}\vec{A}^\top = \vec{A}^\top \vec{A}$
\end{enumerate}
\item
A Markov chain with state space $\brak{0,1,2}$ has transition matrix
$$
\myvec{
\frac12 & \frac12 & 0 \\
\frac12 & \frac12 & 0 \\
\frac13 & \frac13 & \frac13
}.
$$
Which statements are true?
\hfill (ST 2024)
\begin{enumerate}
\begin{multicols}{2}
\item $0$ and $1$ are recurrent
\item $2$ is transient
\item Chain has unique stationary distribution
\item Chain is irreducible
\end{multicols}
\end{enumerate}
\item
$\vec{A}$ is $2\times2$ with $\mathrm{tr}\brak{\vec{A}}=5$, $\det\brak{\vec{A}}=6$. Let the characteristic polynomial of $\brak{\vec{A}+\vec{I}_2}^{-1}$ be $x^2 - b x + c$.  
Find $b/c =$ \underline{\phantom{imagine}} (integer).
\hfill (ST 2024)

