\item Suppose that the characteristic equation of $\vec{M} \in \mathbb{C}^{3\times 3}$ is $\lambda^{3} + \alpha \lambda^{2} + \beta \lambda - 1 = 0$, where $\alpha, \beta \in \mathbb{C}$ with $\alpha + \beta \ne 0$. Which of the following statements is TRUE?
\hfill{\brak{\text{MA 2022}}}
\begin{enumerate}
\begin{multicols}{2}
  \item $\vec{M}\brak{\vec{I} - \beta \vec{M}} = \vec{M}^{-1}\brak{\vec{M} + \alpha \vec{I}}$
\item $\vec{M}\brak{\vec{I} + \beta \vec{M}} = \vec{M}^{-1}\brak{\vec{M} - \alpha \vec{I}}$
\item $\vec{M}^{-1}\brak{\vec{M}^{-1} + \beta \vec{I}} = \vec{M} - \alpha \vec{I}$
\item $\vec{M}^{-1}\brak{\vec{M}^{-1} - \beta \vec{I}} = \vec{M} + \alpha \vec{I}$
\end{multicols}
\end{enumerate}
\item Consider
	\begin{enumerate}[label=\Alph*:,start=16]
		\item  Let $\vec{M} \in \mathbb{R}^{m\times n}$ with $m>n\ge 2$. If $\operatorname{rank}\brak{\vec{M}}=n$, then the system of linear equations $\vec{M}x=0$ has $x=0$ as the only solution.
\item  Let $\vec{E} \in \mathbb{R}^{n\times n}$, $n\ge 2$ be a non-zero matrix such that $\vec{E}^{3}=0$. Then $\vec{I}+\vec{E}^{2}$ is a singular matrix.
\end{enumerate}
Which of the following statements is TRUE?
\hfill{\brak{\text{MA 2022}}}
\begin{enumerate}
\item Both $P$ and $Q$ are TRUE
\item Both $P$ and $Q$ are FALSE
\item $P$ is TRUE and $Q$ is FALSE
\item $P$ is FALSE and $Q$ is TRUE
\end{enumerate}
\item Consider the linear system of equations $\vec{A}\vec{x}=\vec{b}$ with
\begin{align*}
\vec{A} &= \myvec{3 & 1 & 1 \\ 1 & 4 & 1 \\ 2 & 0 & 3}, \quad
\vec{b} = \myvec{2 \\ 3 \\ 4}.
\end{align*}
Which of the following statements are TRUE?

\hfill{\brak{\text{MA 2022}}}

\begin{enumerate}
\item The Jacobi iterative matrix is ~$\myvec{0 & \tfrac{1}{4} & \tfrac{1}{3} \\[4pt]
\tfrac{1}{3} & 0 & \tfrac{1}{3} \\[4pt]
\tfrac{2}{3} & 0 & 0}$
\item The Jacobi iterative method converges for any initial vector
\item The Gauss\textendash Seidel iterative method converges for any initial vector
\item The spectral radius of the Jacobi iterative matrix is less than $1$
\end{enumerate}
\item Let $T \colon \mathbb{R}^{2} \to \mathbb{R}^{2}$ be a linear transformation defined by
\begin{align*}
T\brak{\brak{1,2}} = \brak{1,0} \quad \text{and} \quad T\brak{\brak{2,1}} = \brak{1,1}.
\end{align*}
For $p,q \in \mathbb{R}$, let $T^{-1}\brak{\brak{p,q}} = \brak{x,y}$. Which of the following statements is TRUE?
\hfill{\brak{\text{MA 2022}}}
\begin{enumerate}
\begin{multicols}{2}
\item $x = p - q;\ y = 2p - q$
\item $x = p + q;\ y = 2p - q$
\item $x = p + q;\ y = 2p + q$
\item $x = p - q;\ y = 2p + q$
\end{multicols}
\end{enumerate}
\item Consider $\mathbb{R}^3$ as a vector space with the usual operations of vector addition and scalar multiplication. Let $\vec{x} \in \mathbb{R}^3$ be denoted by $\vec{x} = \brak{x_1, x_2, x_3}$. Define subspaces $W_1$ and $W_2$ by
\begin{align*}
W_1 &:= \{ \vec{x} \in \mathbb{R}^3 \colon x_1 + 2x_2 - x_3 = 0 \},\\
W_2 &:= \{ \vec{x} \in \mathbb{R}^3 \colon 2x_1 + 3x_3 = 0 \}.
\end{align*}
Let $\dim\brak{U}$ denote the dimension of the subspace $U$. Which of the following statements are TRUE?
\hfill{\brak{\text{MA 2022}}}
\begin{enumerate}
\item $\dim\brak{W_1} = \dim\brak{W_2}$
\item $\dim\brak{W_1} + \dim\brak{W_2} - \dim\brak{\mathbb{R}^3} = 1$
\item $\dim\brak{W_1 + W_2} = 2$
\item $\dim\brak{W_1 \cap W_2} = 1$
\end{enumerate}
\item Let $\vec{M}$ be a $3 \times 3$ real matrix such that $\vec{M}^2 = 2\vec{M} + 3\vec{I}$. If $\det \vec{M} = -9$, then the trace of $\vec{M}$ equals \underline{\hspace{2cm}}.
\hfill{\brak{\text{MA 2022}}}
