\begin{enumerate}[label=\thesubsection.\arabic*,ref=\thesubsection.\theenumi]
\item Find the roots of the equation $x^2 + 3x - 10 = 0$ 
\hfill	(10, 2023)
\item If $\alpha, \beta$ are zeroes of the polynomial $x^2 - 1$, then find the value of $\brak{\alpha + \beta}$.

\hfill	(10, 2023)
\item If $ \alpha, \beta $ are the zeroes of the polynomial $ p\brak{x} = 4x^2 - 3x - 7 $, then find $ \frac{1}{\alpha} + \frac{1}{\beta} $.
\hfill	(10, 2023)
\item If one zero of the polynomial $6x^2 + 37x - \brak{k-2}$ is the reciprocal of the other,
    then what is the value of $k$?
\hfill	(10, 2023)
    \item Find the zeroes of the polynomial $p\brak{x} = x ^ 2 + 4x + 3$. 
\hfill	(10, 2023)
\item
Find the sum and product of the roots of the quadratic equation $2x^{2}-9x+4=0$.
\hfill	(10, 2023)
\item
Find the discriminant of the quadratic equation $4x^{2}-5=0$ and hence comment on the nature of roots of the equation.
\hfill	(10, 2023)
\item
If one zero of polynomial $p\brak{x}=6x^{2}+37x-\brak{k-2}$ is reciprocal of the other, then  find the value of $k$.
\hfill	(10, 2023)
\item
Find the value of $p$ for which one root of the quadratic equation $px^{2}-14x+8=0$ is $6$ times the other.
\hfill	(10, 2023)
\item If the sum of zeroes of the polynomial $ p\brak x = 2x^2 - k\sqrt2x+1 $ is${\sqrt2} $, then find the value of $k$. 
\hfill	(10, 2024)
\item Two pipes running together can fill a tank in $11\frac{1}{9}$ minutes. If one pipe takes $5$ minutes more than the other to fill the tank separately, find the time in which each pipe would fill the tank separately.
\hfill	(10, 2016)
%
\item Which of the following quadratic equations has a sum of its roots as  $4$ ?  
\begin{enumerate}
\item $ 2x^2 - 4x + 8 = 0 $                          
\item $ -x^2 - 4x + 4 = 0 $                          
\item $ \sqrt{2}x^2 - \frac{4}{\sqrt{2}}x + 1 = 0 $
\item $ 4x^2 - 4x + 4 = 0 $
\end{enumerate}
\hfill	(10, 2023)
\item A motor boat whose speed is 24 km/hr in still water takes $1$ hour     more to go $32 km$ upstream than to return downstream to the same spot. Find the speed of the stream.
\hfill	(10, 2016)
\item The speed of a boat in still water is 11 km/hr. It can go 12 km upstream and return 
downstream to the original point in 2 hours 45 minutes. Find the speed of the stream.
\hfill	(10, 2006)
\end{enumerate}
